%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{graphicx}
% Render all contact icons at a uniform height (FA solid vs brand glyphs differ in size)
\newcommand{\contacticon}[1]{\raisebox{-0.15em}{\resizebox{!}{0.95em}{#1}}}
% glyphtounicode is pdftex-only; skip under xelatex/lualatex
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
\fi


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\ifdefined\pdfgentounicode
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge Istiaqur Rahman Fuad}
\end{center}

\begin{center}
\small
\contacticon{\faMapMarker*} \, Jamalpur $|$
\contacticon{\faEnvelope} \, \href{mailto:istiaqurrahmanfuad@gmail.com}{istiaqurrahmanfuad@gmail.com} $|$
\contacticon{\faPhone*} \, +880 1865-863271 \\ \vspace{2pt}
\contacticon{\faLinkedin} \, \href{https://www.linkedin.com/in/istiaqfuad}{istiaqfuad} $|$
\contacticon{\faGithub} \, \href{https://github.com/istiaqfuad}{istiaqfuad} $|$
\contacticon{\faGlobe} \, \href{https://istiaqfuad.me}{istiaqfuad.me}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Computer science undergraduate and aspiring backend software engineer specializing in scalable systems and APIs. Comfortable architecting end-to-end web applications and integrating modern AI features as secondary capabilities. Enjoys building robust infrastructure, optimizing databases, and open-sourcing the work.}
\vspace{2pt}

 %-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, TypeScript, C++, C, SQL} \\
     \textbf{Technologies \& Tools}{: Spring Boot, Next.js, FastAPI, PostgreSQL, Redis, RabbitMQ, Docker, Prisma, Stripe, Git} \\
     \textbf{AI / ML}{: PyTorch, Hugging Face, LoRA, LLMs, LangChain, LangSmith, Vector Databases}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Advanced Machine Intelligence Research (AMIR) Lab}{Feb 2026 -- Present}
      {Research Assistant Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Curated and published \textbf{bangla-english-banglish-pairs}, a 2.4M-pair trilingual contrastive dataset (Bangla / Banglish [romanized Bengali] / English) on Hugging Face for low-resource NLP research.}
        \resumeItem{Trained and open-sourced \textbf{TriBne-e5-small}, a trilingual sentence-embedding model for retrieval over code-mixed Bengali text.}
      \resumeItemListEnd

    \resumeSubheading
      {Devcore Technologies}{Feb 2025 -- Apr 2025}
      {Full Stack Developer Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Architected a modular admin dashboard and end-to-end type-safe backend APIs using tRPC and Prisma for an e-commerce platform with a 1,000+ product catalog.}
        \resumeItem{Developed responsive, server-rendered storefront pages with Next.js App Router, improving cross-device usability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Rajshahi}{Jan 2022 -- Expected 2026}
      {B.Sc. in Computer Science and Engineering}{CGPA: 3.58/4.00}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Data Structures \& Algorithms, Object-Oriented Programming, Database Management Systems, Operating Systems, Software Engineering, Artificial Intelligence, Machine Learning}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{EventHub} $|$ \emph{\href{https://eventhub.irflab.tech/}{\color{blue}Live}} $|$ \emph{\href{https://github.com/istiaqfuad/eventhub-project}{\color{blue}GitHub}}}{}

      \resumeItemListStart
        \resumeItem{\textbf{Tools used:} Java, Spring Boot, PostgreSQL, Redis, RabbitMQ, Next.js, Docker, Stripe}
        \resumeItem{Engineered a scalable full-stack ticketing platform (Spring Boot, Next.js) containerized with Docker Compose.}
        \resumeItem{Implemented interactive visual seat selection with Redis holds, Stripe Checkout, and RabbitMQ for async ticket processing.}
      \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{LegalBuddy} $|$ \emph{\href{https://legalbuddy.irflab.tech/}{\color{blue}Live}} $|$ \emph{\href{https://github.com/istiaqfuad/legal-buddy}{\color{blue}GitHub}}}{}

      \resumeItemListStart
        \resumeItem{\textbf{Tools used:} Python, FastAPI, Next.js, Qdrant, sentence-transformers, LLM, Docker}
        \resumeItem{Built a retrieval-augmented generation (RAG) system over Bangladesh legal acts: a FastAPI backend retrieves grounded statute sections from Qdrant and generates cited answers with LLM in a Next.js chat UI.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH AND PUBLICATIONS-----------
\section{Research \& Publications}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{A Trilingual Contrastive Corpus and Parameter-Efficient Recipe for Romanized Bengali Retrieval}}{}

      \resumeItemListStart
        \resumeItem{\textbf{First author}; under review at \textit{Language Resources and Evaluation} (Springer Nature), 2026. \hfill \emph{\href{https://huggingface.co/spaces/istiaqfuad/triBne-e5-small-demo}{\color{blue}Demo}} $|$ \emph{\href{https://github.com/istiaqfuad/triBne-e5}{\color{blue}GitHub}}}
        \resumeItem{LoRA fine-tuned multilingual-e5-small (1\% parameter update, MNRL loss) on a self-built 2.4M-pair trilingual (Bangla / Banglish / English) contrastive corpus for Banglish and cross-script retrieval.}
        \resumeItem{Reached state-of-the-art on Banglish-spelling and cross-script retrieval, lifting cross-script MRR@10 from 0.50 to 0.98 over the base model and beating BGE-M3, LaBSE, and Embedding Gemma.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Courses and Certifications -----------
\section{Courses and Certifications}
\begin{itemize}[leftmargin=0.15in]
    \small{
        \item{Machine Learning Specialization -- Stanford University $|$ DeepLearning.AI (Jul 2023). \href{https://www.coursera.org/account/accomplishments/specialization/certificate/Q6NXEZKR8TMA}{\color{blue}certificate}}
        \vspace{-4pt}
        \item{Deep Learning Specialization -- Stanford University $|$ DeepLearning.AI (Oct 2023). \href{https://www.coursera.org/account/accomplishments/specialization/certificate/B5AQT8YMBQU8}{\color{blue}certificate}}
    }
\end{itemize}

%-----------Achievements and Activities-----------
\section{Achievements and Activities}
\begin{itemize}[leftmargin=0.15in]
    \small{
        \item{\textbf{Award of Merit} -- International Blockchain Olympiad (Oct 2024). \href{https://drive.google.com/file/d/1JBwTW0jXm-M77g4E_a-D2NaJUHX4EyMg/view?usp=sharing}{\color{blue}certificate}}
        \vspace{-4pt}
        \item{\textbf{SDG-9 Silver Medal} -- International Blockchain Olympiad (Oct 2022). \href{https://drive.google.com/file/d/1r5VAn4hBUb7fEbmXG34dBFAzPjVzIfWr/view?usp=sharing}{\color{blue}certificate}}
    }
\end{itemize}
\end{document}
